Example Manuscript Template for a Data Analysis Project

### 2024-03-18 products/manuscript/workspace.qmd
More data work
More data work

write.csv(summarized_data, file = "summarized_dataB.csv", row.names = FALSE)

@@

write.csv(summarized_data, file = "summarized_dataC.csv", row.names = FALSE)

@@

>>>>

write.csv(summarized_dataB, file = "summarized_dataB.csv", row.names = FALSE)

@@

write.csv(summarized_dataC, file = "summarized_dataC.csv", row.names = FALSE)

@@

summarized_dataALL <- WHO_data_fluB %>%
  group_by(WHOREGION, MMWR_WEEKSTARTDATE) %>%
  summarise(
    TOT_INF_ALL = sum(INF_ALL),
    TOT_INF_A = sum (INF_B),
    TOT_INF_B = sum (INF_B)
  )

print(summarized_dataALL)

write.csv(summarized_dataALL, file = "summarized_dataALL.csv", row.names = FALSE)

#WPR Region
WHO_data_fluWPR <- summarized_dataALL %>% filter(WHOREGION == "WPR")
WHO_data_fluWPR <- WHO_data_fluWPR %>% filter(WHOREGION == "WPR")
WHO_data_fluWPR <- na.omit(WHO_data_fluWPR)

print(WHO_data_fluWPR)

write.csv(WHO_data_fluWPR, file = "WHO_data_fluWPR.csv", row.names = FALSE)

# Plot the data using a layered bar graph
plot5A <- ggplot(WHO_data_fluWPR, aes(x = MMWR_WEEKSTARTDATE)) +
  geom_bar(aes(y = TOT_INF_ALL, fill = "INF_ALL"), stat = "identity", color="black", position = "stack") + 
  geom_bar(aes(y = TOT_INF_A, fill = "INF_A"), stat = "identity", color="black", position = "stack") + 
  geom_bar(aes(y = TOT_INF_B, fill = "INF_B"), stat = "identity", color="black", position = "stack") + 
  labs(title = "Influenza Cases Reported to WHO",
       subtitle = "WHOREGION = WPR, 2022-2024 Seasons",
       x = "Week",
       y = "Number of Positive Specimens",
       fill = "Influenza Type") + 
  theme_minimal()

plot5Asave = here("assets", "plot5A.png")
ggsave(plot5Asave, plot5A, width = 10, height = 6, dpi = 300)

#AMR Region
WHO_data_fluAMR <- summarized_dataALL %>% filter(WHOREGION == "AMR")
WHO_data_fluAMR <- WHO_data_fluAMR %>% filter(WHOREGION == "AMR")
WHO_data_fluAMR <- na.omit(WHO_data_fluAMR)

print(WHO_data_fluAMR)

write.csv(WHO_data_fluAMR, file = "WHO_data_fluAMR.csv", row.names = FALSE)

# Plot the data using a layered bar graph
plot5B <- ggplot(WHO_data_fluAMR, aes(x = MMWR_WEEKSTARTDATE)) +
  geom_bar(aes(y = TOT_INF_ALL, fill = "INF_ALL"), stat = "identity", color="black", position = "stack") + 
  geom_bar(aes(y = TOT_INF_A, fill = "INF_A"), stat = "identity", color="black", position = "stack") + 
  geom_bar(aes(y = TOT_INF_B, fill = "INF_B"), stat = "identity", color="black", position = "stack") + 
  labs(title = "Influenza Cases Reported to WHO",
       subtitle = "WHOREGION = AMR, 2022-2024 Seasons",
       x = "Week",
       y = "Number of Positive Specimens",
       fill = "Influenza Type") + 
  theme_minimal()

plot5Bsave = here("assets", "plot5B.png")
ggsave(plot5Bsave, plot5B, width = 10, height = 6, dpi = 300)

#EUR Region
WHO_data_fluEUR <- summarized_dataALL %>% filter(WHOREGION == "EUR")
WHO_data_fluEUR <- WHO_data_fluEUR %>% filter(WHOREGION == "EUR")
WHO_data_fluEUR <- na.omit(WHO_data_fluEUR)

print(WHO_data_fluEUR)

write.csv(WHO_data_fluEUR, file = "WHO_data_fluEUR.csv", row.names = FALSE)

# Plot the data using a layered bar graph
plot5C <- ggplot(WHO_data_fluAMR, aes(x = MMWR_WEEKSTARTDATE)) +
  geom_bar(aes(y = TOT_INF_ALL, fill = "INF_ALL"), stat = "identity", color="black", position = "stack") + 
  geom_bar(aes(y = TOT_INF_A, fill = "INF_A"), stat = "identity", color="black", position = "stack") + 
  geom_bar(aes(y = TOT_INF_B, fill = "INF_B"), stat = "identity", color="black", position = "stack") + 
  labs(title = "Influenza Cases Reported to WHO",
       subtitle = "WHOREGION = AMR, 2022-2024 Seasons",
       x = "Week",
       y = "Number of Positive Specimens",
       fill = "Influenza Type") + 
  theme_minimal()

plot5Csave = here("assets", "plot5C.png")
ggsave(plot5Csave, plot5C, width = 10, height = 6, dpi = 300)
